### 2016-07-25 Chapters/introduction.tex
update intro

%The theory of evolution has deeply changed biology.\\
%\textit{Very broad introduction on how we use evolution to actually make sense of biology}
%
%We are still trying to understand the fundamental forces that shape life in all its diversity.\\
%\textit{Evolution through natural selection is a verbal theory, and people have been trying to formalize it for 200 years.
%It implies working and looking for "the hand of evolution" at several scales, from population to molecular biology.
%It is challenging to translate the mechanisms of natural selection (fitness) at every scale, hence the problems to uncover fundamental properties of life.}
%%Since its invention, huge efforts have been made to put Darwin's theory into equation, in order to clarify our understanding, to see how it apply at different scales (species, populations, cells, molecules...).

Microorganisms exhibits the most fundamental features of life. 
\textit{They are open systems that take energy from the environment around them, and use it to maintain and reproduce their structures.
They live literally everywhere, have the same metabolism, etc...
They represent a perfect model organism for fundamental questions.}

>>>>

Most part of life beauty and diversity is hidden from us in the form of microorganisms.
These small factories are optimized to grab and use energy from their environment, in the form of organic matter, highly reactive chemicals, or even photons [citation trophic].
In that sense, microorganisms exhibit the most fundamental features of life.
They live almost everywhere, sometimes in the strangest possible places [citation space].
This nature of ubiquitous, extremely optimized living systems makes them perfect to unearth the fundamental forces that shape life as we know it.
